Journal and article coverage

### 2025-01-03 analysis/results.Rmd
Redo analysis,

wos_ta_df <- wos_jn_by_year |>
  # only hybrid journals with at least one oa between 2018 - 2023
  filter(issn_l %in% wos_active_jns_with_oa$issn_l) |>
  left_join(wos_jn_ta_by_year, by = c("issn_l", "earliest_year", "pub_type" = "pubtype")) |>
  # Focus on core
  filter(pub_type == "core") |>
  mutate(src = "Web of Science") |>
  select(-pub_type, -p)

@@

scp_ta_df <-  scp_jn_by_year |>
  # only hybrid journals with at least one oa between 2018 - 2023
  filter(issn_l %in% scp_active_jns_with_oa$issn_l) |>
  left_join(scp_jn_ta_by_year, by = c("issn_l", "earliest_year" = "first_pubyear", "pub_type" = "pubtype")) |>
  # Focus on core
  filter(pub_type == "core") |>
  mutate(src = "Scopus") |>
  select(-pub_type, -p)

>>>>

wos_ta_df <- wos_jn_by_year |>
  # only hybrid journals with at least one oa between 2018 - 2023
  filter(issn_l %in% wos_active_jns_with_oa$issn_l) |>
  left_join(wos_jn_ta_by_year, by = c("issn_l", "earliest_year", "pub_type" = "pubtype")) |>
  # Focus on core
  filter(pub_type == "core") |>
  mutate(src = "Web of Science") |>
  select(-pub_type)

@@

scp_ta_df <-  scp_jn_by_year |>
  # only hybrid journals with at least one oa between 2018 - 2023
  filter(issn_l %in% scp_active_jns_with_oa$issn_l) |>
  left_join(scp_jn_ta_by_year, by = c("issn_l", "earliest_year", "pub_type" = "pubtype")) |>
  # Focus on core
  filter(pub_type == "core") |>
  mutate(src = "Scopus") |>
  select(-pub_type)
